### 2013-04-01 exam6/2.tex
Thunk problem.

Computation/thunk problem

>>>>

In most general terms, you can think of a \emph{computation} as something that
\emph{runs} to compute an answer.  To solidify this idea as an interface, a
computation could be represented by an object implementing:

\begin{verbatim}
interface Computation<R> {
  // Run this computation
  R run();
}
\end{verbatim}

\noindent
For example, this computation computes the square of five:

\begin{verbatim}
class TwentyFive implements Computation<Integer> {
  Integer run() { return 5 * 5; }
}
\end{verbatim}

\item Design a computation that when constructed is given a
 \texttt{Computation<Integer>} and a natural number \emph{n}, and when
 run, runs the computation \emph{n} times and produces an array list
of all the results.

\newpage
\item

Computations can be expensive, so it's probably a good idea to avoid
 running them if you can, or if you must run them, run them just once
 and remember the result. Subsequent runs of the computation should
 then just return the remembered value rather than doing any real
 work.

In contemplating the design of a library for such laziness, you should
 realize that this idea of running something at most once and
 remembering its result is itself a computation.  In other words, if
 given a computation, you can make a new computation that will act
 just like the given one, except it will run the given computation at
 most one time.

Design the following class:

\begin{verbatim}
class MaybeOnce<R> implements Computation<R> {
  MaybeOnce(Computation<R> compute) { ... }

  // If this computation has never been run, run
  // compute and produce its result.  Remember
  // this answer for future runs and just return
  // it rather than re-run compute.
  R run();
}
\end{verbatim}
\end{enumerate}

Take care to make sure that if a \texttt{MaybeOnce} computation is not
run, it never runs the inner computation.  For example, 
this program should not blow up (assuming this is the whole program):

\begin{verbatim}
class BlowUp implements Computation<Integer> {
  // Blows up when run
  Integer run() { throw new RuntimeException("KABOOM!"); }
}

// Never run, so never blows up.
new MaybeOnce<Integer>(new BlowUp())
\end{verbatim}
